---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.retina=2,
  fig.width=6,
  fig.height=4,
  fig.path = "man/figures/README-"
)
```

# ggbeeswarm2: Beeswarm-style plots with ggplot2

## Note

This is a fork of ggbeeswarm under active development. 

The `position_beeswarm` function has been 
rewritten and is compatible with R >= v4.0.0. Additionally, `position_beeswarm` 
works almost identically to the `beeswarm` function from the 
[beeswarm](https://cran.r-project.org/web/packages/beeswarm/index.html) package.

For example:

```{r ex, message=FALSE, warning=FALSE}
set.seed(123)
distro <- list(runif = runif(100, min = -3, max = 3), 
               rnorm = rnorm(100))

# beeswarm
beeswarm::beeswarm(distro, 
                   col = 2:3, pch = 16,
                   method = "hex",
                   main = "title")

# ggbeeswarm2
library(dplyr)
library(ggbeeswarm2)

distro2 <- as.data.frame(rev(distro)) %>% 
  tidyr::pivot_longer(
    everything(), 
    values_to = "value", 
    names_to = "variable"
    )

 ggplot2::ggplot(distro2, aes(x = rev(variable), y = value)) + 
   geom_point(position = ggbeeswarm2::position_beeswarm(method = "hex")) + 
   scale_y_continuous(limits = c(-3, 3)) + 
   theme(
     plot.margin = unit(c(0.11, 0.07, 0.11, 0.07), "npc")
   )
```

------
Author: Charlotte Dawson

Original authors: Erik Clarke and Scott Sherrill-Mix
