---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.retina=2,
  fig.width=6,
  fig.height=4,
  fig.path = "man/figures/README-"
)
```

# ggbeeswarm2: Beeswarm-style plots with ggplot2

<!-- badges: start -->
[![R-CMD-check](https://github.com/csdaw/ggbeeswarm2/workflows/R-CMD-check/badge.svg)](https://github.com/csdaw/ggbeeswarm2/actions)
[![Codecov test coverage](https://codecov.io/gh/csdaw/ggbeeswarm2/branch/master/graph/badge.svg)](https://codecov.io/gh/csdaw/ggbeeswarm2?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Note

This is a fork of ggbeeswarm which is in an experimental and unfinished state. 
**Some of changes made here including additional swarming and corral methods 
are now available in the development version of
[ggbeeswarm](https://github.com/eclarke/ggbeeswarm), which is probably what you
should be using.**

I plan on trying out re-writing these functions (again) so that the swarming 
is performed based on the plotting area and size of the plotting character as 
opposed to just the x/y range of the data (as in ggbeeswarm).

The `position_beeswarm` function has been 
rewritten and is compatible with R >= v4.0.0. Additionally, `position_beeswarm` 
works almost identically to the `beeswarm` function from the 
[beeswarm](https://cran.r-project.org/web/packages/beeswarm/index.html) package
with all the additional methods implemented (including the new `compactswarm`).

For example:

```{r ex, message=FALSE, warning=FALSE}
set.seed(123)
distro <- list(runif = runif(100, min = -3, max = 3), 
               rnorm = rnorm(100))

# beeswarm
beeswarm::beeswarm(distro, 
                   col = 2:3, pch = 16,
                   method = "hex",
                   main = "title")

# ggbeeswarm2
library(dplyr)
library(ggbeeswarm2)

distro2 <- as.data.frame(rev(distro)) %>% 
  tidyr::pivot_longer(
    everything(), 
    values_to = "value", 
    names_to = "variable"
    )

 ggplot2::ggplot(distro2, aes(x = rev(variable), y = value)) + 
   geom_beeswarm(method = "hex") + 
   scale_y_continuous(limits = c(-3, 3))
```

------
Author: Charlotte Dawson

Original authors: Erik Clarke and Scott Sherrill-Mix
